\tealeaves: an R package for modeling leaf temperature using energy budgets

### 2019-01-24 ms/ms.tex
biorxiv version

\begin{figure} [t!]
\caption{Extended examples of \tealeaves. Code to generate these examples is provided in the Supporting Information. A. The temperature of smaller leaves is more closely coupled to air temperature. Each line represents a different leaf size (small, dashed line; medium, dotted line; large, solid line) and the leaf-to-air temperature differential ($y$-axis) over a gradient of air temperature ($x$-axis). B. Greater stomatal conductance cools leaves. Each line represents a different stomatal conductance (low, dashed line, 1 [$\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$]; medium, dotted line, 3 [$\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$]; high, solid line, 5 [$\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$]) and the leaf-to-air temperature differential ($y$-axis) over a gradient of irradiance ($x$-axis). C. Forced convection dominates in small leaves; free convection dominates in very large leaves. Leaf size is indicated by line type as in Panel A. Horizontal lines indicate approximate shifts from forced convection ($Ar < 0.1$), mixed convection ($0.1 < Ar < 10$), and free convection ($Ar > 10$). Small leaves always experience forced convection, leading to lower leaf temperature compared to large leaves experiencing free convection. D. Amphistomatous leaves (Stomatal Ratio $\sim$ 0.5) evaporate more than hypo- or hyperstomatous leaves (Stomatal Ratio $\sim$ 0 or 1, respectively), especially under free convection (low wind speed, $u$).}
\label{fig:fig1}
\end{figure}

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $d$                 & \code{leafsize}  & leaf characteristic dimension & m \\
  $\alpha_\mathrm{s}$ & \code{abs\_s}    & absorbtivity of shortwave radiation (0.3 - 4 $\mu$m) & none \\
  $\alpha_\mathrm{l}$ & \code{abs\_l}    & absorbtivity of longwave radiation (4 - 80 $\mu$m) & none \\
  $g_\mathrm{sw}$     & \code{g\_sw}     & stomatal conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^a$ \\
  $g_\mathrm{uw}$     & \code{g\_uw}     & cuticular conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^a$ \\
  $\mathit{sr}$       & \code{logit\_sr} & stomatal ratio (logit transformed) & none \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $P$              & \code{P}       & atmospheric pressure & kPa \\
  $r$              & \code{r}       & reflectance for short-wave irradiance (albedo) & none \\
  $\mathit{RH}$    & \code{RH}      & relative humidity    & none \\
  $S_\mathrm{sw}$  & \code{S\_sw}   & incident short-wave (solar) radiation flux density & W m$^{-2}$ \\
  $T_\mathrm{air}$ & \code{T\_air}  & air temperature      & K \\
  $u$              & \code{wind}    & windspeed            & m s$^{-1}$ \\
  \\
  \multicolumn{4}{l}{\textbf{Physical constants:}} \\
  \\
  $a, b, c, d$     & \code{a, b, c, d} & coefficients for calculating $\mathit{Nu}$ and $\mathit{Sh}$ numbers & none \\
  $c_p$            & \code{c\_p}    & heat capacity of air & 1.01 J g$^{-1}$ K$^{-1}$ \\
  $D_{h,0}$        & \code{D\_h0}   & diffusion coefficient for heat in air at 0 °C & $19.0 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{m,0}$        & \code{D\_m0}   & diffusion coefficient for momentum in air at 0 °C & $13.3 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{w,0}$        & \code{D\_w0}   & diffusion coefficient for water vapour in air at 0 °C & $21.2 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $\epsilon$       & \code{epsilon} & ratio of water to air molar masses & 0.622 \\
  $\mathit{eT}$    & \code{eT}      & exponent for temperature dependence of diffusion & 1.75 \\
  $G$              & \code{G}       & gravitational acceleration & 9.8 m s$^{-2}$ \\
  $R$              & \code{R}       & ideal gas constant & 8.3144598 J mol$^{-1}$ K$^{-1}$ \\
  $R_\mathrm{air}$ & \code{R\_air}  & specific gas constant for dry air & 287.058 J kg$^{-1}$ K$^{-1}$ \\
  $\sigma$         & \code{s}       & Stephan-Boltzmann constant & $5.67 \times 10 ^ {-8}$ W m$^{-2}$ K$^{-4}$ \\

@@

R code for running extended examples. 
\begin{Schunk}
\begin{Sinput}
> # Extended example 1: 
> # leaf size and leaf-to-air temperature differential
> 
> library(tealeaves)
> cs <- make_constants()
> lp  <- make_leafpar(
+   replace = list(
+     leafsize = set_units(c(0.005, 0.1, 0.5), "m")
+   )
+ )
> ep <- make_enviropar(
+   replace = list(
+     S_sw = set_units(660, "W/m^2"),
+     T_air = set_units(seq(278.15, 308.15, 5), "K")
+   )
+ )
> exe1 <- tleaves(lp, ep, cs, progress = TRUE, quiet = TRUE, 
+                 unitless = TRUE, parallel = TRUE)
> 
\end{Sinput}
\end{Schunk}

>>>>

\begin{figure} [t!]
\caption{Extended examples of \tealeaves. Code to generate these examples is provided in the Supporting Information. A. The temperature of smaller leaves is more closely coupled to air temperature. Each line represents a different leaf size (small, dashed line; medium, dotted line; large, solid line) and the leaf-to-air temperature differential ($y$-axis) over a air temperature gradient ($x$-axis). B. Greater stomatal conductance cools leaves. Each line represents a different stomatal conductance (low, dashed line, 1 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$; medium, dotted line, 3 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$; high, solid line, 5 $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$) and the leaf-to-air temperature differential ($y$-axis) over a gradient of incident solar radiation ($x$-axis). C. Forced convection dominates in small leaves; free convection dominates in very large leaves. Leaf size is indicated by line type as in Panel A. Horizontal lines indicate approximate shifts from forced convection ($\mathit{Ar} < 0.1$), mixed convection ($0.1 < \mathit{Ar} < 10$), and free convection ($\mathit{Ar} > 10$). Small leaves always experience forced convection, leading to lower leaf temperature compared to large leaves experiencing free convection. D. Amphistomatous leaves (Stomatal Ratio $\sim$ 0.5) evaporate more than hypo- or hyperstomatous leaves (Stomatal Ratio $\sim$ 0 or 1, respectively), especially under free convection (low wind speed, $u$).}
\label{fig:fig1}
\end{figure}

@@

  \multicolumn{4}{l}{\textbf{Leaf parameters:}} \\
  \\
  $d$                 & \code{leafsize}  & leaf characteristic dimension & m \\
  $\alpha_\mathrm{s}$ & \code{abs\_s}    & absorbtivity of shortwave radiation (0.3 - 4 $\mu$m) & none \\
  $\alpha_\mathrm{l}$ & \code{abs\_l}    & absorbtivity of longwave radiation (4 - 80 $\mu$m) & none \\
  $g_\mathrm{sw}$     & \code{g\_sw}     & stomatal conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^\dagger$ \\
  $g_\mathrm{uw}$     & \code{g\_uw}     & cuticular conductance to water vapour & $\mu$mol m$^{-2}$ s$^{-1}$ Pa$^{-1}$ $^\dagger$ \\
  $\mathit{sr}$       & \code{logit\_sr} & stomatal ratio (logit transformed) & none \\
  \\
  \multicolumn{4}{l}{\textbf{Environmental parameters:}} \\
  \\
  $P$              & \code{P}       & atmospheric pressure & kPa \\
  $r$              & \code{r}       & reflectance for short-wave irradiance (albedo) & none \\
  $\mathit{RH}$    & \code{RH}      & relative humidity    & none \\
  $S_\mathrm{sw}$  & \code{S\_sw}   & incident short-wave (solar) radiation flux density & W m$^{-2}$ \\
  $T_\mathrm{air}$ & \code{T\_air}  & air temperature      & K \\
  $u$              & \code{wind}    & windspeed            & m s$^{-1}$ \\
  \\
  \multicolumn{4}{l}{\textbf{Physical constants:}} \\
  \\
  $a, b, c, d$     & \code{a, b, c, d} & coefficients for calculating $\mathit{Nu}$ and $\mathit{Sh}$ numbers & none \\
  $c_p$            & \code{c\_p}    & heat capacity of air & 1.01 J g$^{-1}$ K$^{-1}$ \\
  $D_{h,0}$        & \code{D\_h0}   & diffusion coefficient for heat in air at 0 °C & $19.0 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{m,0}$        & \code{D\_m0}   & diffusion coefficient for momentum in air at 0 °C & $13.3 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $D_{w,0}$        & \code{D\_w0}   & diffusion coefficient for water vapour in air at 0 °C & $21.2 \times 10^{-6}$ m$^2$ s$^{-1}$ \\
  $\epsilon$       & \code{epsilon} & ratio of water to air molar masses & 0.622 \\
  $\mathit{eT}$    & \code{eT}      & exponent for temperature dependence of diffusion & 1.75 \\
  $G$              & \code{G}       & gravitational acceleration & 9.8 m s$^{-2}$ \\
  $R$              & \code{R}       & ideal gas constant & 8.3144598 J mol$^{-1}$ K$^{-1}$ \\
  $R_\mathrm{air}$ & \code{R\_air}  & specific gas constant for dry air & 287.058 J kg$^{-1}$ K$^{-1}$ \\
  $\sigma$         & \code{s}       & Stephan-Boltzmann constant & $5.67 \times 10 ^ {-8}$ W m$^{-2}$ K$^{-4}$ \\

@@

R code for running extended examples (Fig. \ref{fig:fig1}). This code and that to generate figures are deposited on GitHub (https://github.com/cdmuir/tealeaves-ms).

\begin{Schunk}
\begin{Sinput}
> # Extended example 1: 
> # leaf size and leaf-to-air temperature differential
> 
> library(tealeaves)
> cs <- make_constants()
> lp  <- make_leafpar(
+   replace = list(
+     leafsize = set_units(c(0.005, 0.1, 0.5), "m")
+   )
+ )
> ep <- make_enviropar(
+   replace = list(
+     S_sw = set_units(660, "W/m^2"),
+     T_air = set_units(seq(278.15, 308.15, 5), "K")
+   )
+ )
> exe1 <- tleaves(lp, ep, cs, progress = TRUE, quiet = TRUE, 
+                 unitless = TRUE, parallel = TRUE)
> 
\end{Sinput}
\end{Schunk}
